---
title: "masters poster"
author: "James Lee"
date: "4/20/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

Predicting Book Ratings using Regression Methods

Analysis paralysis occurs when overthinking a situation stops a solution from being reached.
It can happen in situations where the number of choices is so large that it
is difficult to reason about.
For example, trying to figure out the next book to read can be difficult because the catalog 
of all possible books is very large, and this can result in one never choosing a book at all.
Creating a model to predict a user's rating of a book can alleviate this difficulty of choice.
In this project, we create a book rating prediction model that can be used to recommend
a new book to read.

```{r}
book_data <- read.csv("toptags10/book_data.csv")
ratings <- read.csv("goodbooks-10k/ratings.csv")
user_data <- 
  ratings %>% 
  filter(user_id == 30944) %>% 
  merge(book_data, by = "book_id") %>% 
  select(-c(book_id, user_id, goodreads_book_id))
```

```{r}
lm10 <- lm(rating ~ 0 + ., data=user_data, )
summary(lm10)
```

